timesliced_random_cell_selection

### 2018-11-15 src/timesliced_random_cell_selection.Rmd
creation of minimum convex polygon for constraining background points

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("raster", "dplyr", "data.table", "sp")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

What I want to do is for each time slice, create a list of all cells (xyz), then remove the ones where observations occuredand create a .csv with the name of the level being worked on

>>>>

# Package dependencies
You can install and load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). Note this function checks to see if the packages are installed first before loading.

```{r pre-install & load packages, include=FALSE}
packages <- c("raster", "dplyr", "data.table", "sp", "adehabitatHR")
source("../src/ipak.R")
ipak(packages)
```

@@

The area covered by these points are huge -much larger than the distribution of my presence points. Ideally I need to constrain the area where the background points are selected from to match the entire range of the species. The most common method for this is to use a minimum convex hull to estimate the species range, and then use that area to constrain the background point selection.
Note I am a little worried that I may loose some of the edge data as they are centroids of cells...

```{r}
mcpbase <- read.csv("../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno_env.csv", header = TRUE)
mcpbase_xy <- mcpbase[ , c("decimalLongitude.1", "decimalLatitude.1")] # This is to tell R where the coordinates are (in column 18 and 19). Note that the column order needs to be longitude, latitude
mcpbase_sp <- SpatialPointsDataFrame(coords = mcpbase_xy, data = mcpbase, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
mcp_capelin_100 <- mcp(mcpbase_sp[ , 12], percent = 100) #12 is the column with the species name in (the id for the species)
plot(mcp_capelin_100)
```

oh tres exciting. Let's overlay the occurrence points on that

```{r}
plot(mcp_capelin_100)
points(mcpbase_sp$decimalLongitude.1, mcpbase_sp$decimalLatitude.1)
```

ok yea, i guess.... still wondering about those edge areas....anyway

What I want to do is for each time slice, create a list of all cells (xyz), then remove the ones where observations occurred and create a .csv with the name of the level being worked on
